
# Empirical Results

```{r setup, include = FALSE}
source("misc/load_libraries.R")
knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE)
```

```{r load data}
data <- read_rds("data/final/data.RDS")
```

```{r}
data %>% filter(sale_type == "New Sale" & ctrl_prop_type != "Executive Condominium") %>% select(project_name, starts_with("facil")) %>% filter(is.na(facil_bbq) | is.na(facil_swp) | is.na(facil_tennis) | is.na(facil_basketball) | is.na(facil_gym) | is.na(facil_functionrm) | is.na(facil_jacuzzi) | is.na(facil_sauna)) %>% distinct(project_name)
```


```{r function to extract coefficients}
# because I'm only running log-linear regressions, I set it to return a string
# with a percentage rounded to 2 decimal places
extract_coef <- function(model, var) {
    coefs <- coef(model)
    result <- (coefs[var] * 100) %>% as.double() %>% round(2) %>% as.character()
    return(str_c(result, "%"))
}
```

```{r function to extract r squared}
extract_r2 <- function(model) {
    r2 <- summary(model)$r2
    return(round(r2, 3))
}
```

```{r set up models}
make_reg_formula <- function(...) {
    input_list <- list(...)
    result <- ""
    for (v in input_list) {
        for (ele in v) {
            result <- str_c(result, ele, sep = " + ")
        }
    }
    result <- str_sub(result, 4, str_length(result)) # remove additional " + " at the front
    return(result)
}
reg <- function(..., area_fe = "", time_fe = "", s = subs) {
    reg_formula <- make_reg_formula(...)
    if (time_fe != "") {
        reg_formula <- str_c(reg_formula, " + ", time_fe)
    }
    if (area_fe != "") {
        reg_formula <- str_c(reg_formula, " | ", area_fe)
    }
    felm(formula(reg_formula), data = data, subset = f_eval(s, data))
}
summary2 <- function(reg_mdl) {
    summ <- summary(reg_mdl, robust = TRUE)
    summ$coefficients <- summ$coefficients[!str_detect(dimnames(summ$coefficients)[[1]], time_fe),]
    return(summ)
} 
base_reg <- "ln_price_psm ~ award_dummy"
did_dummy <- "award_after"
controls <- c("ctrl_prop_type", "ctrl_ln_area", "ctrl_freehold", "ctrl_floor", "ctrl_floor2", 
              "ctrl_firstfloor", "ctrl_topfloor", "ctrl_dist_mrt", "ctrl_yrs_to_completion",
              "facil_bbq", "facil_swp", "facil_tennis", "facil_basketball", "facil_gym",
              "facil_functionrm", "facil_jacuzzi", "facil_sauna")
placebo_interaction <- "placebo_interaction"
conquas_vars <- c("conquas_score")
area_fe <- "ctrl_postal_first4"
time_fe <- "sale_ym"
subs <- ~ sale_type == "New Sale" & ctrl_prop_type != "Executive Condominium"
subs_placebo <- ~ sale_type == "Resale" & ctrl_prop_type != "Executive Condominium" & placebo_flag == 1
keep_coefs <- function(...) {
    mdls <- list(...)
    covariates <- mdls %>% 
        map(~.x$coefficients) %>% 
        map(dimnames) %>% 
        map(~.[[1]]) %>% 
        unlist()
    covariates <- covariates[
        !str_detect(covariates, time_fe) & !str_detect(covariates, "(Intercept)") & !str_detect(covariates, "facil_")] %>% 
        unique()
    if (any(str_detect(covariates, "placebo"))) {
        covariates <- c(
            covariates[covariates %in% c("award_dummy", placebo_interaction)],
            covariates[!covariates %in% c("award_dummy", placebo_interaction)])
    }
    return(covariates)
}
label_coefs <- function(lst) {
    str_replace_all(lst, c(
        "award_dummy" = "GM Award",
        "award_after" = "GM x After GM",
        "ctrl_ln_area" = "ln(Area (sqm))",
        "ctrl_freehold" = "Freehold",
        "ctrl_floor2" = "Floor$^{2}$",
        "ctrl_floor" = "Floor",
        "ctrl_firstfloor" = "First Floor",
        "ctrl_topfloor" = "Top Floor",
        "ctrl_hdb_buyer" = "HDB Buyer",
        "ctrl_prop_type" = "Property Type: ",
        "ctrl_lease" = "Lease Type: ",
        "ctrl_dist_mrt" = "Distance to MRT (km)",
        "ctrl_yrs_to_completion" = "Years to Completion",
        "placebo_interaction" = "GM x GM After New Sale",
        "conquas_score$" = "CONQUAS Score",
        "conquas_score_cat61-70" = "CONQUAS Score: 61-70", 
        "conquas_score_cat71-80" = "CONQUAS Score: 71-80",
        "conquas_score_cat81-90" = "CONQUAS Score: 81-90", 
        "conquas_score_cat> 90" = "CONQUAS Score: > 90", 
        "conquas_score_catMissing" = "CONQUAS Score: Missing",
        "conquas_truncated" = "CONQUAS Score Censored"
    ))
}
extract_ses <- function(model) {
    summ <- summary2(model)
    se <- summ$coefficients[,2]
    return(se)
}
```

```{r}
data[f_eval(subs, data),] %>% 
    group_by(award_dummy, award_after) %>% 
    summarise(transactions = n(), projects = n_distinct(project_name))
```

```{r naive model}
naive_mdl <- reg(base_reg)
summary2(naive_mdl)
```

```{r naive model with controls}
naive_mdl_with_controls <- reg(base_reg, controls, area_fe = area_fe)
summary2(naive_mdl_with_controls)
```

```{r model with controls and year-month FE}
naive_mdl_with_controls_ymfe <- reg(base_reg, controls, area_fe = area_fe, time_fe = time_fe)
summary2(naive_mdl_with_controls_ymfe)
```

## Results from "Naive" Models

Table \@ref(tab:naiveresults) reports the regression results from the "basic" hedonic models. The most basic model specified by equation \@ref(eq:naive) suggests that the GM award provides a `r extract_coef(naive_mdl, "award_dummy")` price premium over non-GM properties. However, this model suffers from omitted variable bias and also has a very low $R^2$ of `r extract_r2(naive_mdl)`. The model specified by equation \@ref(eq:naivewithcontrols) which adds hedonic characteristics, locational controls (4-digit postal code dummies) and condominium/apartment facilities shows a GM award effect of `r extract_coef(naive_mdl_with_controls, "award_dummy")`. Because this model adds a significant number of variables, the $R^2$ also increases significantly to `r extract_r2(naive_mdl_with_controls)`. After controlling for property market trends using year-month dummies, this effect changes to `r extract_coef(naive_mdl_with_controls_ymfe, "award_dummy")`.

The coefficients of the hedonic characteristics are all expected. For instance, condominiums are more expensive compared to comparable apartments, higher floors command higher prices but suffer from diminishing returns. Units on the first and top floors of any block are cheaper than comparable units on other floors because these typically have unliveable space (first floors have patios and top floors have roof terraces). Properties further away from the closest MRT station also sell for lesser.

```{r naive models results, include = TRUE, results = "asis"}
vars_to_keep <- keep_coefs(naive_mdl_with_controls_ymfe)
labels <- label_coefs(vars_to_keep)
area_fe_line <- c("4-digit Postal Code Fixed Effects", "No", "Yes", "Yes")
time_fe_line <- c("Year-Month Dummies", "No", "No", "Yes")
condo_facils_line <- c("Condo Facilities Dummies", "No", "Yes", "Yes")
ses <- map(list(naive_mdl, naive_mdl_with_controls, naive_mdl_with_controls_ymfe), extract_ses)
stargazer(naive_mdl, naive_mdl_with_controls, naive_mdl_with_controls_ymfe, 
          type = "latex", title = "Effects of GM Award on Price",
          keep = vars_to_keep, order = vars_to_keep, covariate.labels = labels,
          dep.var.labels = "Natural log of Price psm", header = FALSE,
          add.lines = list(area_fe_line, time_fe_line, condo_facils_line), 
          se = ses, digits = 3, label = "naiveresults", no.space = TRUE)
```

```{r DID base model}
did_base_mdl <- reg(base_reg, did_dummy, controls, area_fe = area_fe, time_fe = time_fe)
summary2(did_base_mdl)
```

```{r DID model with CONQUAS}
did_with_conquas <- reg(base_reg, did_dummy, controls, conquas_vars, area_fe = area_fe, time_fe = time_fe)
summary2(did_with_conquas)
```

```{r function to calculate reduction in observations}
reduction_in_obs <- function(mdl1, mdl2) {
    n1 <- summary(mdl1)$N
    n2 <- summary(mdl2)$N
    diff <- ((1 - (n1/n2)) * 100) %>% 
        round(0) %>% 
        format(big.mark = ",", scientific = FALSE)
    return(str_c(diff, "%"))
}
```

```{r DID model with CONQUAS categorical}
did_with_conquas_cat <- reg(base_reg, did_dummy, controls, "conquas_score_cat", area_fe = area_fe, time_fe = time_fe)
summary2(did_with_conquas_cat)
```

## Results from DID Models

The above models were further improved by using a DID methodology as outlined in the previous section. The results from the DID specifications are reported in Table \@ref(tab:didresults). Controlling for hedonic characteristics, availability of facilities, locational effects and year-month effects, the announcement of GM award increases a property's price by `r extract_coef(did_base_mdl, "award_after")`. GM rated properties are also higher quality than non-GM rated ones, having a `r extract_coef(did_base_mdl, "award_dummy")` premium before they receive the award. 

Adding CONQUAS score as a regressor changes the premium associated with the GM award announcement to `r extract_coef(did_with_conquas, "award_after")`, indicating that quality is an important factor in determining housing prices. This implies that the previous models suffered from omitted variable bias, due to the announcement of award being correlated with the unobserved quality of the building (which can be captured by the CONQUAS score). 

Unfortunately, since CONQUAS scoring is optional, many buildings do not apply for it; about `r reduction_in_obs(did_with_conquas, did_base_mdl)` of the observations were dropped. This might cause selection problems. This can be solved by categorising the CONQUAS score into bands, and including a category for missing scores. Doing so could also reduce noise as it is unlikely that people are able to take into account the exact scores into pricing decisions. This model shows that the GM announcement is associated with a `r extract_coef(did_with_conquas_cat, "award_after")` increase in price of a GM rated property. It also shows that higher CONQUAS scores are associated with higher prices, especially when compared to the lowest scores of 61-70. Properties with missing CONQUAS scores also command a premium over properties with CONQUAS scores of 61-70. This indicates that property buyers really do not like low quality properties.

```{r DID results, include = TRUE, results = "asis"}
vars_to_keep <- c(keep_coefs(did_with_conquas), "conquas_score_cat71-80", "conquas_score_cat81-90", 
                  "conquas_score_cat> 90", "conquas_score_catMissing")
labels <- label_coefs(vars_to_keep)
area_fe_line <- c("4-digit Postal Code Fixed Effects", "Yes", "Yes", "Yes")
time_fe_line <- c("Year-Month Dummies", "Yes", "Yes", "Yes")
condo_facils_line <- c("Condo Facilities Dummies", "Yes", "Yes", "Yes")
ses <- list(did_base_mdl, did_with_conquas, did_with_conquas_cat) %>% map(extract_ses)
stargazer(did_base_mdl, did_with_conquas, did_with_conquas_cat,
          type = "latex", title = "Difference-in-difference Models",
          keep = vars_to_keep, order = vars_to_keep, covariate.labels = labels,
          dep.var.labels = "Natural log of Price psm", header = FALSE,
          add.lines = list(area_fe_line, time_fe_line, condo_facils_line), 
          se = ses, digits = 3, label = "didresults", no.space = TRUE)
```

```{r placebo model}
placebo_mdl <- reg(base_reg, placebo_interaction, controls, area_fe = area_fe, time_fe = time_fe, s = subs_placebo)
placebo_mdl_with_conquas <- reg(base_reg, placebo_interaction, controls, "conquas_score", area_fe = area_fe, time_fe = time_fe, s = subs_placebo)
placebo_mdl_with_conquas_cat <- reg(base_reg, placebo_interaction, controls, "conquas_score_cat", area_fe = area_fe, time_fe = time_fe, s = subs_placebo)
summary2(placebo_mdl)
summary2(placebo_mdl_with_conquas)
summary2(placebo_mdl_with_conquas_cat)
```

## Results from Placebo DID

Finally, a placebo DID model is also run, to ensure that GM rated and non-GM rated properties are comparable. The specification is described in the previous section. Running the model on `r format(summary(placebo_mdl)$N, big.mark = ",", scientific = FALSE)` resale transactions shows a positive but insignificant DID coefficient. This result indicates that there is no selection bias that is not controlled for by the regressors in the DID model with CONQUAS scores.

```{r placebo results, include = TRUE, results = "asis"}
vars_to_keep <- c(keep_coefs(placebo_mdl_with_conquas), "conquas_score_cat61-70", "conquas_score_cat71-80", "conquas_score_cat81-90", 
                  "conquas_score_cat> 90", "conquas_score_catMissing")
labels <- label_coefs(vars_to_keep)
area_fe_line <- c("4-digit Postal Code Fixed Effects", "Yes", "Yes", "Yes")
time_fe_line <- c("Year-Month Dummies", "Yes", "Yes", "Yes")
condo_facils_line <- c("Condo Facilities Dummies", "Yes", "Yes", "Yes")
ses <- list(placebo_mdl, placebo_mdl_with_conquas, placebo_mdl_with_conquas_cat) %>% map(extract_ses)
stargazer(placebo_mdl, placebo_mdl_with_conquas, placebo_mdl_with_conquas_cat,
          type = "latex", title = "Placebo Difference-in-difference Tests",
          keep = vars_to_keep, order = vars_to_keep, covariate.labels = labels,
          dep.var.labels = "Natural log of Price psm", header = FALSE,
          add.lines = list(area_fe_line, time_fe_line, condo_facils_line), 
          se = ses, digits = 3, label = "placeboresults", no.space = TRUE)
```

```{r}
problem_projects <- data %>% 
    filter((placebo_resale_before_gm == 1) & (project_name != "NA")) %>% 
    distinct(project_name) %>% 
    .$project_name
last_new_sales <- data %>% 
    filter((project_name %in% problem_projects) & (sale_type == "New Sale")) %>% 
    group_by(project_name) %>% 
    arrange(desc(sale_ym)) %>% 
    filter(row_number() == 1) %>% 
    mutate(yr_last_new_sale = as.integer(str_sub(award_ym, 1, 4))) %>% 
    select(project_name, yr_last_new_sale)
first_resales <- data %>% 
    filter((project_name %in% problem_projects) & (sale_type == "Resale")) %>% 
    group_by(project_name) %>% 
    arrange(sale_ym) %>% 
    filter(row_number() == 1) %>% 
    mutate(award_yr = as.integer(str_sub(award_ym, 1, 4)), 
           yr_first_resale = as.integer(str_sub(sale_ym, 1, 4))) %>% 
    select(project_name, top_year, award_yr, yr_first_resale)
garbage_sales <- first_resales %>% 
    left_join(last_new_sales, by = "project_name") %>% 
    select(project_name, award_yr, top_yr = top_year, yr_last_new_sale, yr_first_resale) %>% 
    mutate(top_before_2005 = top_yr < 2005,
           resale_before_last_new_sale = yr_first_resale < yr_last_new_sale,
           resale_before_top = yr_first_resale < top_yr)
```


\newpage