---
title: "Clean Green Mark Dataset"
output: #html_notebook
---

This script will clean the greenmark dataset in preparation for merging with the transactions dataset. The objective is to prepare a dataset with a unique key that is the project name, so that I can merge it with the transactions dataset from REALIS. The process is as follows: 

1. Check for missing postal codes and fix them
1. Remove properties that are definitely not private residential properties (e.g. HDB, university residences, mixed developments with no residential units)
1. Try to match on postal code, and get the corresponding project name from the transactions dataset.
1. If there is no match in postal code and hence no corresponding project name, I will get all the possible project names using the postal code in the URA geocoding API. Hopefully because the REALIS dataset is from URA, using the geocoding API from URA's Onemap will yield project names that match the project names in the REALIS data. **This will likely not be perfect, and this will result in some projects not being correctly classified as Greenmark award recipients.**
1. The final dataset to be merged will be identified by a project name, and have information on what type of greenmark award, as well as the award year


```{r setup}
source("misc/load_libraries.R")
```

```{r load data}
greenmark <- read_rds("data/raw/greenmark/greenmark.RDS")
transactions <- read_rds("data/raw/private/non-landed.RDS")
```

Looks like only The Glades does not have a valid postal code (I don't care about PSA Maintenance Base because that has no residential blocks).

```{r check missing postal codes}
greenmark %>% filter(is.na(postal_code))
```

So we can just replace its postal code with one that we can find from the transactions dataset.

```{r replace postal code for The Glades Condo}
glades_postal_code <- transactions %>% filter(project_name == "THE GLADES") %>% .$postal_code %>% .[1]
greenmark <- greenmark %>% mutate(postal_code = replace(postal_code, project_name == "The Glades", glades_postal_code))
greenmark %>% filter(project_name == "The Glades")
```

We don't care about recertifications

```{r remove recertifications}
greenmark <- greenmark %>% filter(!str_detect(str_to_lower(project_name), "certification"))
greenmark
```

Since there are a sizable number of mixed developments with no specification of whether or not they contain residential units, we'll look at them first.

```{r check how many mixed devs}
mixed_devs <- greenmark %>% filter(type_of_building == "Mixed Development")
mixed_devs
```

Get rid of all mixed developments that don't have a residential component: I first grab the building descriptions of buildings classified as "Mixed Development" by scraping Grenemark Buildings Directory again, then print out the descriptions. I read the descriptions of these buildings and determine which ones are mixed developments with residential units. From there I can subset the data.

```{r grab building description to determine if it contains residential}
get_description <- Vectorize(function(bldg_id) {
    page <- read_html(GET(str_c("https://www.bca.gov.sg/green_mark/KnowledgeResources/BuildingDirectoryDetail.aspx?id=", bldg_id)))
    
    details <- page %>% 
        html_node("td+ td tr:nth-child(1) tr~ tr+ tr td") %>% # grab details section
        html_text() %>% 
        str_trim() %>% 
        str_split("Project Description:") %>% .[[1]] %>% .[2] %>% # get rid of preceding details
        str_split("Green Features:") %>% .[[1]] %>% .[1] %>% # get rid of green features section
        str_trim() %>% str_replace_all("\\r\\n", " ")
    
    return(details)
})
mixed_devs <- mixed_devs %>% mutate(description = get_description(id))
mixed_devs %>% write_tsv("misc/mixed_devs.tsv") # to print out from excel
```

```{r filter residential only}
residential_greenmark <- greenmark %>% 
    filter((type_of_building != "Mixed Development") | (id %in% c("946", "669", "1606", "1639", "1140", "1141", "650", "907")))
residential_greenmark
```

I observe some residences that are HDB flats or university residences - since I am dealing only with private housing transactions, I'll remove them first.

```{r filter out HDB and uni residences}
residential_greenmark <- residential_greenmark %>% 
    mutate(project_name = str_to_upper(project_name)) %>% 
    filter(!str_detect(project_name, "(^BLK|HALL OF RESIDENCE|KENT VALE|FACULTY HOUSING|UNIVERSITY)"))
residential_greenmark
```


Now I can start merging the greenmark dataset with the transactions dataset

```{r find matches on postal code}
merged <- residential_greenmark %>% 
    left_join(transactions, by = "postal_code") %>% 
    distinct(year_award, award, project_name.x, project_name.y, postal_code)
merged
```


```{r find which matches have no proper project name in dataset}
merged %>% filter(is.na(project_name.y))
```

```{r get project names from URA geocoding API}
get_project_name_from_ura <- Vectorize(function(postal_code) {
    api <- "https://developers.onemap.sg/commonapi/search?searchVal=singapore+<pcode>&returnGeom=Y&getAddrDetails=Y&pageNum=1"
    info <- fromJSON(file = str_replace(api, "<pcode>", postal_code))
    
    if (info$found == 0) {
        return(NA_character_)
    }
    
    results <- info$results
    building_names <- map(results, ~.["BUILDING"]) %>% unlist()
    return(building_names)
})
merged_wo_projname <- merged %>% 
    filter(is.na(project_name.y)) %>%
    select(-project_name.x, -project_name.y) %>% 
    mutate(project_name = get_project_name_from_ura(postal_code)) %>% 
    unnest() %>% 
    distinct(year_award, award, project_name)
merged_wo_projname
```

Building = "NIL" sounds about right.

```{r replace NIL project name}
merged_wo_projname <- merged_wo_projname %>% 
    mutate(project_name = replace(project_name, project_name == "NIL", "16 LAKESHORE VIEW"))
merged_wo_projname
```

Next I can get the final dataset that can be merged with the transactions dataset

```{r combine datasets with and without matching project names in transactions dataset}
merged_with_projname <- merged %>% 
    filter(!is.na(project_name.y) & project_name.y != "N.A.") %>% 
    select(project_name = project_name.y, year_award, award)
greenmark_cleaned <- merged_with_projname %>% bind_rows(merged_wo_projname)
```

```{r save cleaned greenmark dataset}
greenmark_cleaned %>% write_rds("data/intermediate/greenmark_cleaned.RDS")
```



