---
title: "Scrape IDs for Green Mark Buildings"
output: #html_notebook
---

# Purpose of Scraping IDs

The [BCA Green Mark Buildings Directory](https://www.bca.gov.sg/green_mark/KnowledgeResources/BuildingDirectory.aspx) contains both Singapore and foreign buildings. The website has a simple URL structure to scrape the information from single buildings, where the URL is just a prefix and an ID for the building. Since some foreign buildings might have a postal code structure identical to Singapore, it is less risky to first get all the building IDs of Singapore buildings, then loop through the IDs to scrape the actual data.

```{r setup}
library(RSelenium)
library(tidyverse)
library(stringr)
library(rvest)
```


```{r scrape-all}
get_greenmark_ids <- function() {
    
    # Function to scrape all the building IDs to loop through in the main
    # scraping script. Does this by browsing the buildings directory (by
    # default, it selects Singapore buildings) when we click on "Search
    # Listing". Then we can find out how many pages of listings there is,
    # and loop through that number; grabbing the building IDs from the links
    # in each page. Stores all this in the data frame that is returned.

    #addCap <- list(phantomjs.page.settings.userAgent = "Mozilla/5.0 (Windows NT 6.1; WOW64; rv:29.0) Gecko/20120101 Firefox/29.0")
    #browser <- remoteDriver(browserName = "phantomjs", extraCapabilities = addCap)
    browser <- remoteDriver(browserName = "chrome")
    browser$open()
    browser$navigate("https://www.bca.gov.sg/green_mark/KnowledgeResources/BuildingDirectory.aspx")
    
    # get only residential buildings
    browser$findElement(using = "xpath", "//*[@id=\"map_accordion\"]/ul/li[4]/a/div")$clickElement()
    Sys.sleep(1)
    browser$findElement(using = "xpath", "//*[@id=\"chkBuilding16\"]")$clickElement()
    
    browser$findElement(using = "xpath", "//*[@id=\"imgBtnSearchListing\"]")$clickElement()
    
    no_buildings <- browser$findElement(
        using = "xpath", 
        "//*[@id=\"Form1\"]/table/tbody/tr[1]/td/table/tbody/tr/td/span[2]"
        )$getElementText() %>% 
        str_match("(\\d+)( results)") %>% 
        .[,2] %>% 
        as.integer()
    no_pages <- ceiling(no_buildings / 10)
    
    all_ids <- tibble()
    for (i in 1:no_pages) {
        curr_page <- browser$getPageSource()[[1]]
        page <- curr_page %>% read_html()
        
        links <- page %>% html_nodes("a") %>% map(str_trim)
        if (length(links) == 0) {
            next()
        }
        links <- tibble(links = links) %>% unnest()
        
        ids <- links$links %>% 
            str_match_all("(id=)([0-9]+)") %>% 
            map(~.[,3]) %>% 
            unlist()
        if (length(ids) == 0) {
            next()
            }
        ids <- tibble(ids = ids)
        all_ids <- all_ids %>% bind_rows(ids)
        
        browser$executeScript(str_c("__doPostBack('gdSearchData', 'Page$", i+1, "')"), args = list())
        next_page <- browser$getPageSource()[[1]]
        while (next_page == curr_page) {
            print("waiting")
            Sys.sleep(0.5)
            next_page <- browser$getPageSource()[[1]]
        }
            
        #Sys.sleep(2)
    }
    
    browser$close()
    return(all_ids)
}


```

```{r}
ids <- get_greenmark_ids()
```

```{r}
ids %>% distinct(ids) %>% saveRDS(file = "data/raw/greenmark/greenmark_ids.RDS")
```


